%%
%% This is file `xampl-intro.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% vakthesis.dtx  (with options: `xampl-intro')
%%
%% IMPORTANT NOTICE:
%%
%% For the copyright see the source file.
%%
%% Any modified versions of this file must be renamed
%% with new filenames distinct from xampl-intro.tex.
%%
%% For distribution of the original source see the terms
%% for copying and modification in the file vakthesis.dtx.
%%
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%% xampl-intro.tex  Приклад вступу до дисертації
% Приклад ненумерованого розділу
\chapter*{Introduction}


\paragraph{Relevance}
Simulation. It is one of the most powerful tools for making right choices. In software, it can be seen almost everywhere, yet scientific computing and game design created the most favorable conditions for this mechanism to evolve. However, there are many issues that are caused by a necessity for most simulations to be constantly refined. In game design that brought the whole industry to spend massive amount of money on content generation: assets, storylines, etc.
All of them are usually handmade for a simple reason: there is no affordable AI system that can reproduce such diversity and integrity in creative tasks like a human. On the other hand, there is an enormous amount of people spending their time to make narratives. The ability to automate this process even a bit can make it possible to create games much faster.
\paragraph{Practical implementation of the results}

The results can be used to implement a framework for a diverse set of simulations.
However, a framework that is described in this paper is optimized for usage in game design area. The main purpose of the designed framework is to provide means of creating the realistic simulation and data extraction. Another application of the framework is to test experimental game mechanics without its full specification, or by specifying the mechanics on demand during the simulation process.

\paragraph{Individual contribution}
Several abstract architectures for a storyline simulation framework type were introduced:
\begin{itemize}
 \item \textbf{Model0} and \textbf{Model0V} abstract architectures were developed for describing the functionality of the framework;
 \item \textbf{Model1} was introduced to clarify some questions that might arise during the implementation of the framework.
\end{itemize}
